model_lba

### 2024-12-06 model_lba.Rmd
small typo fix to model loading

```{r}
tmp=load("models/ea/modelKN.RData")
cores=length(sKN)

@@

# Make diagnostics, tweak layout as desired
pdf("figures/ea/modelKN_chains.pdf",height=6,width = 8)
plot.dmc(hKN,hyper=TRUE,pll.chain=TRUE) 
plot.dmc(hKN,hyper=TRUE,layout=c(3,3))
plot.dmc(hKN,hyper=TRUE,layout=c(4,4),p.prior=pp.prior)
dev.off()

>>>>

```{r}
tmp=load("models/ea/dmKN.RData")
cores=length(sKN)

@@

# Make diagnostics, tweak layout as desired
pdf("figures/ea/modelKN_chains.pdf",height=6,width = 8)
plot.dmc(hKN,hyper=TRUE,pll.chain=TRUE) 
plot.dmc(hKN,hyper=TRUE,layout=c(3,3))
plot.dmc(hKN,hyper=TRUE,layout=c(3,3),p.prior=pp.prior)
dev.off()
